Carbonate chemistry at Ny-Ålesund

### 2022-07-20 awipev-CO2.Rmd
output of desc stats still absent

range_month <-
  d_all %>%
  dplyr::select(sal_fb_mix) %>% 
#  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
    #group_by(montht) %>%
#tbl_summary(by = montht, missing = "no",
tbl_summary(missing = "no",
            type = all_continuous() ~ "continuous2",
            statistic = all_continuous() ~ c(
      "{mean} ({sd})",                             # line 1: mean and SD
      "{median} ({p25}, {p75})",                   # line 2: median and IQR
      "{min}, {max}")    ) %>% 
  add_n() %>% 
  modify_header(label = "**Variable**") %>%
  bold_labels()# %>% 
  #as_gt()
range_month

# range_month <-
#   d_all %>%
#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
#   group_by(montht) %>%
#   my_skim()
# print(range_month, include_summary = FALSE, width = 100)
```
```{r example}
library(survival)
patient_characteristics <-
  trial %>%
  select(trt, age, grade, response) %>%
  tbl_summary(by = trt)  
patient_characteristics
```

>>>>

range_month <-
  d_all %>%
  dplyr::select(sal_fb_mix) %>% 
#  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
    #group_by(montht) %>%
#tbl_summary(by = montht, missing = "no",
tbl_summary(missing = "no",
            type = all_continuous() ~ "continuous2",
            statistic = all_continuous() ~ c(
              "{mean}",    # line 1: mean and SD
              "{median}",
             # "{p25}, {p75})",  # line 2: median and IQR
              "{min}",
              "{max}")
) #%>% 
  #add_n() %>% 
  #modify_header(label = "**Variable**") %>%
  #bold_labels()# %>% 
  #as_gt()
range_month

# range_month <-
#   d_all %>%
#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
#   group_by(montht) %>%
#   my_skim()
# print(range_month, include_summary = FALSE, width = 100)
```
